Exploring United States Housing Affordability

### 2016-08-10 paper/Paper.Rmd
minor changes

##Graphical findings

```{r, echo = F, fig.cap="Median Burden across Years and Household sizes"}
clean_years <- read_csv("../clean_data/clean_years.csv")

@@

region_1 <- regions_tbl[2:7,] %>% 
  gather(key = region, value = state, 1:2) %>% 
  slice(1:9) %>%
  mutate(region = 1)

region_2 <- regions_tbl[10:15,] %>% 
  gather(key = region, value = state, 1:2) %>% 
  mutate(region = 2)

@@

@@

ggplot() + theme(panel.background = element_rect(fill = 'white', colour = 'white'))
```

>>>>

#Graphical findings

```{r, echo = F, fig.cap="Median Burden across Years and Household sizes"}
#Read in the cleaned data
clean_years <- read_csv("../clean_data/clean_years.csv")

@@

region_1 <- regions_tbl[2:7, ] %>% 
  gather(key = region, 
         value = state, 1:2) %>% 
  slice(1:9) %>%
  mutate(region = 1)

region_2 <- regions_tbl[10:15, ] %>% 
  gather(key = region, 
         value = state, 1:2) %>% 
  mutate(region = 2)

@@

#Factoring for the region faceting

@@

ggplot() + 
  theme(panel.background = element_rect(fill = 'white', 
                                        colour = 'white'))
